\documentclass[11pt,letterpaper,twoside]{article}
\usepackage[hmarginratio=1:1,top=1in,bottom=.75in,left=1.5in,right=1.5in]{geometry}

\usepackage{etoolbox}
\usepackage{ccicons}
\usepackage{fontawesome5}
\usepackage{marginnote}
\usepackage{sidenotes}

\usepackage{needspace}
\usepackage[defaultlines=3,all]{nowidow}
\raggedbottom

\usepackage{ragged2e}
\setlength{\RaggedRightParindent}{0em}
\RaggedRight

\usepackage[singlespacing]{setspace}

\usepackage[none]{hyphenat}

\usepackage{parskip}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.6em plus 0.2em minus 0.1em}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

% ==========================
% = Language & Date Format =
% ==========================

\usepackage[english]{babel}
\usepackage{currfile}

% ==================
% = Colors & Fonts =
% ==================

\usepackage[table]{xcolor}
\definecolor{OffBlack}{HTML}{191919}
\definecolor{Maroon}{HTML}{800000}
\definecolor{TarHeelBlue}{HTML}{4b9cd3}
\definecolor{HopkinsBlue}{HTML}{002D72}
\definecolor{RacingGreen}{HTML}{004225}

\usepackage{fontspec}
\setmainfont{Athelas}[Mapping=tex-text]
\setsansfont{Adelle Sans}[Mapping=tex-text]
\setmonofont[Scale=0.90]{LFT Etica Mono}

% font style for margin notes
%\renewcommand{\marginfont}{\color{RacingGreen}\sffamily\scriptsize}

% smaller sizes for footnotes & captions
%\renewcommand{\footnotesize}{\scriptsize}
%\renewcommand{\captionsize}{\small\itshape}

% =======================
% = Headers and Footers = 
% =======================

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot{}
\fancyfoot[C]{}
\fancyfoot[R]{\tiny\texttt{ Revised: \today}}
\fancyfoot[L]{}
\fancyhead[CE]{\textsc{Professional Responsibility}}
\fancyhead[CO]{\textsc{Elon University School of Law}}
\fancyhead[LE]{\textsc{\thepage}}
\fancyhead[LO]{\textsc{Fall 2025}}
\fancyhead[RE]{\textsc{Prof. Fink}}
\fancyhead[RO]{\textsc{\thepage}}

% =========
% = Lists =
% =========

\usepackage{enumitem}
\setlistdepth{6}
\setlist[itemize]{leftmargin={1.5em}}
\providecommand{\tightlist}{%
\setlength{\itemsep}{0em}\setlength{\parskip}{0em}\setlength{\itemindent}{0em}}

% ============
% = Headings =
% ============

\usepackage[compact]{titlesec}
% \titlespacing*{<command>}{<left>}{<before-sep>}{<after-sep>}
\titlespacing*{\section}{0em}{0em}{.5em}
\titlespacing*{\subsection}{0em}{2em}{.5em}
\titlespacing*{\subsubsection}{0em}{1.5em}{.5em}
\titlespacing*{\paragraph}{0em}{1em}{0em}
\titlespacing*{\subparagraph}{0em}{.2em}{0em}

\setcounter{secnumdepth}{0}

% H1
\titleformat{\section}[block]
  {\LARGE\sffamily\color{Maroon}}
  {}
  {0em}
  {}

% H2
\titleformat{\subsection}[block]
  {\needspace{9\baselineskip}\Large\sffamily\color{Maroon}}
  {}
  {0em}
  {}
% H3
\titleformat{\subsubsection}[block]
  {\needspace{6\baselineskip}\large\rmfamily\bfseries}
  {\thesubsection}
  {0em}
  {}
% H4
\titleformat{\paragraph}[block]
  {\footnotesize\sffamily}
  {\thesubsubsection}
  {0em}
  {}
% H5
\titleformat{\subparagraph}[block]
  {\footnotesize\rmfamily}
  {}
  {0em}
  {}

% ==========
% = Quotes =
% ==========

\usepackage{csquotes}

\AtBeginEnvironment{quote}{\footnotesize\itshape} 

\renewenvironment{quote}{%
   \list{}{%
     \leftmargin2em   % this is the adjusting screw
     \rightmargin\leftmargin\parsep .1em }
   \item\relax
}
{\endlist}

% ==========
% = Tables =
% ==========

\usepackage{longtable,booktabs,array}
%\setlength\heavyrulewidth{0pt}
\usepackage{multirow}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
% set table font size & space between rows
\renewcommand{\arraystretch}{1.5}
\AtBeginEnvironment{longtable}{\footnotesize}

% =============
% = Footnotes = 
% =============

\usepackage[hang,flushmargin]{footmisc} 

%\renewcommand{\footnotesize}{\fontsize{9pt}{11pt}\selectfont} %use to change size of footnotes

% ==============
% = Hyperlinks =
% ==============

\usepackage[unicode=true]{hyperref}
\hypersetup{%
  colorlinks=true,
  allcolors=HopkinsBlue,
  breaklinks=true,
  pdfusetitle=true,
  pdfauthor={Eric M. Fink},
  pdftitle={Syllabus},
    pdfsubject={Professional Responsibility},
      pdfproducer={LateX via pandoc},
  pdfcreator={LateX via pandoc}
}

% ===============================
% ===== BEGIN DOCUMENT ==========
% ===============================

\begin{document}\thispagestyle{empty}

% Sets default font color without overriding hyperlink colors
\color{OffBlack}

% \maketitle

\section{Professional Responsibility}

\begin{footnotesize}
\subparagraph{Elon University School of Law}
\subparagraph{Fall 2025}
\subparagraph{Room 207}
\subparagraph{Mondays \& Wednesdays, 9:45--10:45 am}
\subparagraph{\url{emfink.net/PR}}
\vspace{1em}

\paragraph{Professor}
\subparagraph{Eric M. Fink} 
\subparagraph{efink@elon.edu}
\subparagraph{336.279.9334} 
\subparagraph{Office Hours: {\url{calendly.com/emfink/}}}

\vspace{1em}

\subparagraph{Teaching Assistant:}
\subparagraph{Holden Bryant}
\subparagraph{hbryant4@elon.edu}
\end{footnotesize}

\vspace{1em}

\needspace{1\baselineskip}

\subsection{Description}\label{description}

This course is intended to acquaint students with the organization and
regulation of the legal profession, the nature of the attorney-client
relationship, and the duties that attorneys owe to clients and others.
Upon successfully completing the course, students should be familiar
with the ABA Model Rules of Professional Conduct and other sources of
law governing the legal profession, and be able to apply these rules to
issues that arise in legal practice. The course will also help prepare
students for the \href{https://www.ncbex.org/exams/mpre/}{Multistate
Professional Responsibility Examination (MPRE)}, but will not cover all
of the topics tested on that exam.

\subsection{Materials}\label{materials}

\subsubsection{Required}\label{required}

\href{https://emfink.net/PR}{Professional Responsibility: An Open-Source
Casebook} (v.4.1 2025). Available at
\href{https://www.emfink.net/PR/}{emfink.net/PR}.

\subsubsection{Suggested}\label{suggested}

Grace M. Giesel,
\href{https://cap-press.com/books/isbn/9781611636208/Mastering-Professional-Responsibility-Second-Edition}{Mastering
Professional Responsibility} (2d ed., Carolina Academic Press 2015).

\subsection{Policies}\label{policies}

\subsubsection{Grading}\label{grading}

Your grade will be based on a final examination consisting of multiple
choice questions, similar in format to the
\href{https://www.ncbex.org/exams/mpre}{Multistate Professional
Responsibility Examination (MPRE)}. You will receive a copy of the Rules
of Professional Conduct to use during the exam, which will otherwise be
closed-book/closed-notes. The exam will take place during the Fall exam
period (date and time TBA)

\subsubsection{Attendance}\label{attendance}

Elon Law School has adopted the following attendance policy for all
courses:

\begin{quote}
The Law School administers a policy that a student maintain regular and
punctual class attendance in all courses in which the student is
registered, including externships, clinical courses, or simulation
courses. Faculty members will give students written notice of their
attendance policies before or during the first week of class. These
policies may include, but are not limited to: treating late arrivals,
early departures, and/or lack of preparation as absences; imposing grade
or point reductions for absences, including assigning a failing grade or
involuntarily withdrawing a student from the class; and any other
policies that a professor deems appropriate to create a rigorous and
professional classroom environment.

In case of illness or emergency, students may contact the Office of
Student and Professional Life, which will then notify the student's
instructors. A student may notify the faculty member directly of a
planned absence and should refer to individual faculty members regarding
any policy that may apply. In the case of prolonged illness or
incapacity, the student should contact the
\href{https://www.elon.edu/u/law/students/}{Office of Student Life}.
\end{quote}

You should let me know (in advance if feasible) if you are unable to
attend class, will arrive late, or must leave early. I do not require an
explanation of the reason, nor do I require a doctor's note or other
documentation.

\subsubsection{Disability
Accommodations}\label{disability-accommodations}

For disability accommodation requests, contact the
\href{https://www.elon.edu/u/academics/koenigsberger-learning-center/disabilities-resources/homepage/graduate-student-resources/}{Elon
Disability Services Office}.

\subsubsection{Honor Code}\label{honor-code}

The Law School
\href{https://www.elon.edu/u/law/students/honor-code/}{honor code}
applies to all activities related to your law school study, including
conduct during class and examinations.

\subsection{Schedule \& Reading
Assignments}\label{schedule-reading-assignments}

(\emph{Note:} This class will not meet on Sept.~24)

\subsubsection{1. The Legal Profession \& Regulation of
Lawyers}\label{the-legal-profession-regulation-of-lawyers}

\emph{Casebook}, Chap. 1; \emph{Geisel}, Chap. 1 \& 2\footnote{The
  Giesel hornbook readings are optional. You may find them helpful to
  get an overview of the topics covered.}

\textbf{Sept.~3:} Regulatory Authorities; Misconduct \& Discipline,
\emph{Casebook} §§ 1.1 \& 1.2

\textbf{Sept.~8:} Bar Admission; Unauthorized Practice of Law; Law Firms
\emph{Casebook} §§ 1.3-1.5

\subsubsection{2. Advertising \&
Solicitation}\label{advertising-solicitation}

\emph{Casebook}, Chap. 2; \emph{Geisel}, Chap. 45 \& 46

\textbf{Sept.~10:} Advertising; Solicitation, \emph{Casebook} §§ 2.1 \&
2.2

\subsubsection{3. The Attorney-Client
Relationship}\label{the-attorney-client-relationship}

\emph{Casebook}, Chap. 3; \emph{Giesel Chap.} 4 \& 8-14

\textbf{Sept.~15:} Establishing an Attorney-Client Relationship;
Prospective Clients; Declining \& Terminating Representation,
\emph{Casebook} §§ 3.1, 3.2, \& 3.3

\textbf{Sept.~17:} Scope of Representation \& Allocation of Authority,
\emph{Casebook} §§ 3.4

\textbf{Sept.~22:} Clients with Diminished Capacity; Organizational
Clients, \emph{Casebook} §§ 3.5 \& 3.6

\textbf{Sept.~29 \& Oct.~1:} Attorney Fees \& Client Property,
\emph{Casebook} §§ 3.7 \& 3.8

\subsubsection{4. The Duty of Care}\label{the-duty-of-care}

\emph{Casebook}, Chap. 4; \emph{Geisel}, Chap. 5-7 \& 24

\textbf{Oct.~6 \& 8:} Competence, Diligence, \& Communication;
Malpractice, \emph{Casebook} §§ 4.1 \& 4.2

\textbf{Oct.~13:} Ineffective Assistance of Counsel; Malpractice in
Criminal Cases, \emph{Casebook} §§ 4.3 \& 4.4

\subsubsection{5. Confidentiality \&
Privileges}\label{confidentiality-privileges}

\emph{Casebook}, Chap. 5; \emph{Geisel}, Chap. 15-16

\textbf{Oct.~15 \& 20:} The Duty of Confidentialty, \emph{Casebook} §
5.1

\textbf{Oct.~22:} Attorney-Client Privilege \& Work-Product,
\emph{Casebook} § 5.2 \& 5.6

\subsubsection{6. Conflicts of Interest}\label{conflicts-of-interest}

\emph{Casebook}, Chap. 6; \emph{Geisel}, Chap. 17-23

\textbf{Oct.~27:} Conflicts Between Current Clients, \emph{Casebook} §
6.1 \& 6.2

\textbf{Oct.~29:} Conflicts Involving the Lawyer's Business \& Personal
Interests, \emph{Casebook} § 6.2

\textbf{Nov.~3 \& 5:} Conflicts Involving Former Clients; Imputed
Conflicts, \emph{Casebook} § 6.3 \& 6.4

\subsubsection{7. Duties in Litigation}\label{duties-in-litigation}

\emph{Casebook}, Chap. 7; \emph{Geisel}, Chap. 26-33

\textbf{Nov.~10 \& 12:} Truthfulness; Fairness \& Impartiality;
Extrajudicial Statements \emph{Casebook} Chap. 7, §§ 7.1-7.3

\textbf{Nov.~17:} Prosecutorial Misconduct, \emph{Casebook} § 7.4

\subsubsection{8. Interactions with
Non-Clients}\label{interactions-with-non-clients}

\emph{Casebook}, Chap. 8; \emph{Geisel}, Chap. 35-37

\textbf{Nov.~19 \& 24:} General Rules; Represented Persons;
Unrepresented Persons, \emph{Casebook} §§ 8.1, 8.2, \& 8.3

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\textbf{Dec.~8:} Final Exam

\end{document}
